Conference output

### 2018-05-31 Report/arne-conference.Rmd
More arnes comments

block_measure <- function(df, value){
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = sum(block3-block4, na.rm = T)/sum(block4+block3, na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = sum(block1-block4, na.rm = T)/sum(block4+block1, na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}
```
Block 43 diff is now flipped to (block4 - block3)/(block4 + block3) and block41 is the forth and first.

@@

ggplot(df, aes(x = condition, y = block34.diff, fill = condition)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  geom_errorbar(aes(ymin=block34.diff-block34.se, ymax=block34.diff+block34.se), 
                width=.2, position=position_dodge(.9)) 
  ylab("Mean sum of errors improvement from block 3 to 4")

@@

>>>>

block_measure <- function(df, value){
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = mean((block3-block4)/(block4+block3), na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = mean((block1-block4)/(block1+block4), na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}
```
Block 43 diff is now flipped to (block4 - block3)/(block4 + block3) and block41 is the forth and first.

@@

ggplot(df, aes(x = condition, y = block34.diff, fill = condition)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  geom_errorbar(aes(ymin=block34.diff-block34.se, ymax=block34.diff+block34.se), 
                width=.2, position=position_dodge(.9)) +
  ylab("Mean sum of errors improvement from block 3 to 4")

@@

## Independent comparisons

```{r, echo=F}
df_wide <- dcast(condition_all_sums, condition + id ~ exp_block_id, value.var = "mean.distance")
colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
df_wide$diff14 <- (df_wide$block1-df_wide$block4)/(df_wide$block1+df_wide$block3)
```

1 to 4 improvement comparison between VE-real and real-real
```{r}
t.test(df_wide$diff14[df_wide$condition=="ve-real"],df_wide$diff14[df_wide$condition=="real-real"])

1 to 4 improvement comparison between VR-real and real-real
```{r}
t.test(df_wide$diff14[df_wide$condition=="vr-real"],df_wide$diff14[df_wide$condition=="real-real"])  
```

1 to 4 improvement comparison between VR-real and VE-real
```{r}
t.test(df_wide$diff14[df_wide$condition=="vr-real"],df_wide$diff14[df_wide$condition=="ve-real"])
```
